\documentclass[12pt,a4]{article}
\input{preamble}




\setcounter{section}{7}

\section{Spanning Trees}



\begin{itemize}
 \item Homework assignment published on Monday, 2018-04-16
 \item Submit questions and first solution by Sunday, 2018-04-22, 12:00, by email to me and the TAs.
 \item Submit your final solution by Sunday, 2018-04-29.
\end{itemize}

\subsection{Minimum Spanning Trees}


\input{h8-JiayiSong}



\subsection{Counting Special Functions}

\input{h8-YimingLiu}



\input{h8-zyy}

The next two exercises use a bit of probability theory. Suppose we want to sample a random
tree on $[n]$. That is, we want to write a little procedure (say in Java) that uses randomness and outputs
a tree $T$ on $[n]$, where each of the $n^{n-2}$ trees has the same probability of 
appearing. 

\begin{exercise}
   Sketch how one could write such a procedure. Don't actually write program code, just
   describe it informally. You can assume you have access to a random generator
   \texttt{randomInt($n$)} that returns a function in $\{1,\dots,n\}$ as well
   as \texttt{randomReal()} that returns a random real number from the interval $[0,1]$.
\end{exercise}

Clearly, a tree $T$ on $[n]$ has at least $2$ and at most $n-1$ leaves. But how 
many leaves does it have on average? For this, we could use your tree sampler from the previous
exercise, run it 1000 times and compute the average. However, it would be much nicer to have 
a closed formula.

\begin{exercise}
  Fix some vertex $u \in [n]$. If we choose a tree $T$ on $[n]$ uniformly at random,
  what is the probability that $u$ is a leaf?
   What is the expected number of leaves of $T$?
\end{exercise}

\begin{exercise}
  For a fixed vertex $u$, what is the probability that $u$ has degree $2$?
\end{exercise}



\end{document}
